---
title: "Efficiency Analysis"
author: "Lily Gullett -- lilysgullett@outlook.com"
output:
  html_document:
    theme: flatly
    code_folding: show
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_doctument:
      toc: yes
      toc_depth: 3
---
```{r, setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, fig.align = 'left')
knitr::opts_knit$set(root.dir = "../data")
options(width = 88)
library(magrittr)
```





### version: `r Sys.Date() %>% format(format="%B %d, %Y")`

<!-- this is where the DOI would go  [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3675991.svg)](https://doi.org/10.5281/zenodo.3675991)
-->


#### [GitHub repository](https://github.com/LilyGullett/recruitPilot){target="_blank"}
###

***
This is the working analysis pipeline to analyze data generated from the recruit pilot study of the time it took to take inventory and scans and assess differences in the inventory speed between trained and untrained eyes as well as between scans and manual inventory. 

***

### All analyses performed with R version `r getRversion()`


# Basic setup of R environment
***
## Loading required packages
For the following analyses we will require the use of a number of different R packages. Most of which can be sourced from CRAN, but some must be downloaded from GitHub. We can use the following code to load in the packages and install any packages not previously installed in the R console. 


```{r,packages, include = TRUE, message = FALSE, warning = FALSE, results = 'hide'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("ggplot2", "googlesheets4", "dplyr", "officer","reshape2", "stringr", "flextable", "gridExtra", "ggpubr", "Rmisc", "rcompanionf", "RColorBrewer", "googledrive", "gdata", "readxl", "DescTools","patchwork", "FSA", "rstatix", "tidyverse", "lme4", 'PMCRMplus', "EnvStats", "emmeans", "MuMIn", "sjstats", "lmerTest", "gargle", "httpuv")

```

# Importing Data
***
## We are downloading this dataset from our GoogleDrive folder. We will be using the package `googledrive`. Each GoogleDrive file has a unique ID that does not change throughout the lifespan of the document, even if the file name is changed. This ID is housed in the file's URL. 
Example: docs.google.com/spreadsheets/d/FILE_ID_GOES_HERE/other_information/. Below you will copy and paste that into the function `drive_download` within `as_id`. This will save the file locally in the specified path (in this case our data folder) and you will import the folder as you normally would. Downloading it this way decreases the potential human error when downloading, moving folders, renaming, saving etc and ensures that the most up to date file is being utilized. 

# Here we are importing data from google drive

```{r, LoadingData, include = TRUE}
# drive_auth <- function(email = gargle::gargle_oauth_email(),
#                        path = NULL,
#                        scopes = "https://www.googleapis.com/auth/drive",
#                        cache = gargle::gargle_oauth_cache(),
#                        use_oob = gargle::gargle_oob_default(),
#                        token = NULL) { ... }


 data <- drive_download(
 as_id("1xyLtNN61HYvXYIhD-B4Eca8BPCuEwTftA4936MfwM-w"),
   path = "../data/recruitDataset.xlsx", 
   overwrite = TRUE)

timeData <- read_excel("../data/recruitDataset.xlsx", sheet = 4)

timeData

```

# Graphing the photos taken at each timepoint
***
## I added rack colors to the data in order to make them easily distinguishable. After that I created a graph which plots the number of photos taken at each timepoint separated by rack.

```{r, graphing, include=TRUE}
#Adding rack colors, green being for the mixed batch of plugs. 
#timeData$rackColor[timeData$rackNumber == '1'] <- "pink"
#timeData$rackColor[timeData$rackNumber == '2'] <- "purple"
#timeData$rackColor[timeData$rackNumber == '3'] <- "green"

#Plot that compares number of photos per rack over the days post-settlement which shows the new colors 
timeData1 <- timeData %>% 
  select(timepoint, rack, trainedEyeTime, untrainedEyeTime, scanTime) %>% 
  pivot_longer(cols = trainedEyeTime:scanTime,
               names_to = 'type', 
               values_to = 'inventoryTime') %>% 
mutate_at(c('type'), as.factor)

#Creating a plot with both trained and untrained eye counts on it
comparingPlot <- ggplot(timeData1, aes(x = timepoint, y = inventoryTime)) + geom_bar(position = 'dodge', stat = 'identity', aes(fill = type))+
  facet_grid(.~type, scales = 'free_x')+ 
  xlab("Timepoint (weeks)") + ylab("Time Taken (minutes)") +
    ggtitle("Comparing Inventory Efficiency") +
    theme_bw()
comparingPlot <- comparingPlot+theme(
    axis.text.x = element_text(size = 25, colour = "black", vjust = 0.5, hjust = 0.5, face= "bold"), 
    axis.title.x = element_text(size = 30, face = "bold"),
    axis.title.y = element_text(size = 30, face = "bold"), 
    axis.text.y = element_text(colour = "black", size = 24, face = "bold"),
    legend.title = element_text(size = 30, face = "bold"), 
    legend.text = element_text(size = 25, face = "bold", colour = "black"), 
    panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"),
    panel.background = element_rect(fill = '#F5F5F5'), 
    plot.title = element_text(size = 37, face = "bold"), 
    axis.line = element_line(colour = "black"), 
    axis.ticks = element_line(color="black"), 
    text = element_text(size=40, color="black"), 
    legend.position = "right")
comparingPlot

ggsave("../figures/timeComparison.png", plot = comparingPlot, width = 15, height = 10, units = "in", dpi = 600)


#Creating a dataframe with the outliers (T0) removed
timeData2 <- timeData1 %>%  
filter (timepoint != "0")
head (timeData2)

#kruskal-wallis test for significance between inventory method time
kruskal.test(inventoryTime ~ type, data = timeData2)

test <- dunn_test(timeData2, inventoryTime~type, "bonferroni", TRUE)

#Average time per inventory type throughout all timepoints except T0
averageData <- timeData %>% 
  filter (timepoint != "0") %>%
  group_by(trainedEyeTime, untrainedEyeTime, scanTime) %>%
  summarise(trainedEye = ave(trainedEyeTime)) %>% 
  summarise(untrainedEye = ave(untrainedEyeTime)) %>% 
  summarise(scan = ave(scanTime))
  


#Scan time per timepoint graph
scanPlot <- ggplot(timeData, aes(x = timepoint, y = scanTime)) + geom_bar(position = 'dodge', stat = 'identity', aes(fill = timepoint))+
  facet_grid(.~rack, scales = 'free')+ xlab("Timepoint (weeks)") + ylab("Time Taken (minutes)") +
    ggtitle("Scan Time Per Rack Per Timepoint") +
    theme_bw()
scanPlot <- scanPlot+theme(
    axis.text.x = element_text(size = 25, colour = "black", vjust = 0.5, hjust = 0.5, face= "bold"), 
    axis.title.x = element_text(size = 30, face = "bold"), 
    axis.title.y = element_text(size = 30, face = "bold"), 
    axis.text.y = element_text(colour = "black", size = 24, face = "bold"),
    legend.title = element_text(size = 30, face = "bold"), 
    legend.text = element_text(size = 25, face = "bold", colour = "black"), 
    panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"),
    panel.background = element_rect(fill = '#F5F5F5'), 
    plot.title = element_text(size = 37, face = "bold"), 
    axis.line = element_line(colour = "black"), 
    axis.ticks = element_line(color="black"), 
    text = element_text(size=40, color="black"), 
    legend.position = "right")
ggsave("../figures/scanTimePerTimepoint.png", plot = scanPlot, width = 15, height = 10, units = "in", dpi = 600)
scanPlot

trainedPlot <- ggplot(timeData, aes(x = timepoint, y = trainedEyeTime)) + geom_bar(position = 'dodge', stat = 'identity', aes(fill = timepoint))+
  facet_grid(.~rack, scales = 'free')+ xlab("Timepoint (weeks)") + ylab("Time Taken (minutes)") +
    ggtitle("Trained Eye Inventory Time Per Rack Per Timepoint") +
    theme_bw()
trainedPlot <- trainedPlot+theme(
    axis.text.x = element_text(size = 25, colour = "black", vjust = 0.5, hjust = 0.5, face= "bold"), 
    axis.title.x = element_text(size = 30, face = "bold"),
    axis.title.y = element_text(size = 30, face = "bold"), 
    axis.text.y = element_text(colour = "black", size = 24, face = "bold"),
    legend.title = element_text(size = 30, face = "bold"), 
    legend.text = element_text(size = 25, face = "bold", colour = "black"), 
    panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"),
    panel.background = element_rect(fill = '#F5F5F5'), 
    plot.title = element_text(size = 37, face = "bold"), 
    axis.line = element_line(colour = "black"), 
    axis.ticks = element_line(color="black"), 
    text = element_text(size=40, color="black"), 
    legend.position = "right")
ggsave("../figures/trainedTimePerTimepoint.png", plot = trainedPlot, width = 15, height = 10, units = "in", dpi = 600)

#The code for the untrained eye time per rack per timepoint
untrainedPlot <- ggplot(timeData, aes(x = timepoint, y = untrainedEyeTime)) + geom_bar(position = 'dodge', stat = 'identity', aes(fill = timepoint))+
  facet_grid(.~rack, scales = 'free')+ xlab("Timepoint (weeks)") + ylab("Time Taken (minutes)") +
    ggtitle("Untrained Eye Inventory Time Per Rack Per Timepoint") +
    theme_bw()
untrainedPlot <- untrainedPlot+theme(
    axis.text.x = element_text(size = 25, colour = "black", vjust = 0.5, hjust = 0.5, face= "bold"), 
    axis.title.x = element_text(size = 30, face = "bold"),
    axis.title.y = element_text(size = 30, face = "bold"), 
    axis.text.y = element_text(colour = "black", size = 24, face = "bold"),
    legend.title = element_text(size = 30, face = "bold"), 
    legend.text = element_text(size = 25, face = "bold", colour = "black"), 
    panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"),
    panel.background = element_rect(fill = '#F5F5F5'), 
    plot.title = element_text(size = 37, face = "bold"), 
    axis.line = element_line(colour = "black"), 
    axis.ticks = element_line(color="black"), 
    text = element_text(size=40, color="black"), 
    legend.position = "right")
ggsave("../figures/untrainedTimePerTimepoint.png", plot = untrainedPlot, width = 15, height = 10, units = "in", dpi = 600)

```
#Creating new columns
***
## Creating columns that compare the differences in time taken between trained eye physical inventory, untrained eye physical inventory, and scans.

```{r, adding columns, include = TRUE}

#Adding columns that contain the absolute value of the difference between the trained eye count time and untrained eye count time, trained eye count time and scan time counts, and untrained eye count time and scan time
timeData1 <- timeData %>%
  mutate(
    trainedVsUntrained = abs(trainedEyeTime - untrainedEyeTime),
    trainedVsScan = abs(trainedEyeTime - scanTime), 
    untrainedVsScan = abs(untrainedEyeTime - scanTime )
  ) %>% 
  mutate(var(9), as.factor)

timeData1$rackColor <- as.factor(timeData1$rackColor)

#Outputs the head of the data to see if it added correctly
head(timeData1)

```
# Graphing the 
***
## I created a graph which plots 

```{r, graphing, include=TRUE}

#melting the dataframe into long format to plot all
timeData2 <- reshape2::melt(data = timeData, c(1,2,3,4,8,9), variable.name = "type", value.name = "time" )

#Plotting the different methods by timepoint and time taken each rack
practicePlot <- ggplot(timeData2, aes(x = timePoint, y = time, color = rackNumber))+
  geom_point()+
  facet_grid(.~type, scales = 'free')+ 
    xlab("Timepoint") + ylab("Time (Minutes)") +
    ggtitle("Time per Method") 
  
practicePlot

practicePlotColor <- ggplot(timeData2, aes(x = timePoint, y = time, color = as.factor(rackColor)))+
  geom_point() + 

  facet_grid(.~type, scales = 'free')+ 
  scale_fill_manual(name="Rack Color",labels=c('Pink', 'Purple', 'Alternating'),values = c("pink","#9FA0FF", "green")) + 
    xlab("Timepoint") + ylab("Time (Minutes)") +
    ggtitle("Time per Method") 


#ggsave("../figures/practicePhotoPerTimepoint.png", plot = practicePlot, width = 15, height = 10, units = "in", dpi = 600)
practicePlotColor


```

```{r}


kwTime <- timeData1 %>% 
  filter(timepoint != "0")
kruskal.test(inventoryTime ~ type, data = kwTime)
timeDunn <- dunn_test(kwTime, inventoryTime~type, p.adjust.method = 'bonferroni', detailed = TRUE)



```









